---
title: "Cabbages"
author: "Antonio"
date: "Summer 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 The cabbages data from the MASS package is loaded into a data frame called veggy. We are looking for the difference in the average amount of Vitamin C in Cabbages and if cultivation techniques play a significant role in the cabbages content. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?

$H_0$: No difference in the Vitamin C content of cabbages based on cultivation techniques

$H_A$: There is a difference in Vitamin C content of cabbages based on cultivation techniques

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The response variable (how much Vitamin C) is numerical; The input variable is categorical. We have a Num ~ Cat.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

The graphical results show that when Cultivation techniques move from c52 to c39 we can see a large increase in Vitamin C content within the cabbages, going from an average Vitamin C content of fifty up towards sixty-five. There is a significant difference between the two different cultivation techniques and they drastically affect the Vitamin C content within the cabbages. Making the Cultivation technique c52 the best.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

According to the numerical results they show how for the Cultivation technique c39, it carries a Vitamin C content of fifty-two while the cultivation technique c52 carries a Vitamin C content of sixty-four. Making the cultivation technique c52 the best technique to achieve the highest Vitamin C content within cabbages. There is a significant difference between the two cultivation techniques when measuring the Vitamin C content within the cabbages.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

i

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
